The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
Removed more emphs

		With the second generation onion routing used in Tor, a modified algorithm is used to derive the encryption keys, called \emph{telescoping path-building}, which also provides perfect forward secrecy. This algorithm is described in section \ref{ss:tor_circuit}.

@@

	\subsection{Low-resource routing attacks}
		Another possible attack on the anonymity of Tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}. With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resources, thus compromising the anonymity Tor provides. The idea of this attack is that a malicious Onion router can lie about its bandwidth, thus advertising a much higher bandwidth than it actually has. Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry and exit node are chosen is high.

@@

		Rahman \cite{rahman2009survey} proposes several options to build incentives in a peer-to-peer network. The first proposal that is described is the so called \emph{Warm-glow Model}. This model determines the percentage of free-rides based on the probabilistic population distribution. If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.

@@

		The third proposal is \emph{Reciprocity-Based Schemes}. Using this approach, a peer maintains a behavior history of other peers in the network. These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity. The former are more suitable for longer relationships between peers. The latter is more scalable but they rely on third party and must handle trust issues themselves.

@@

		Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) \cite{backes2012ace}. This protocol uses telescoping, which means that the initiator negotiates session keys with each successive hop in the circuit. There are several proposals for more efficient key exchange methods. One of them is \emph{ACE}, an one-way authenticated key exchange protocol. The authors of this methods claim to have a 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the Onion Routers. ACE requires clients to send one extra element in the key exchange. This does not introduce any overhead however, because the element fits in the unused space in a cell.

@@

	\subsection{Gnutella} % ~2000
		Gnutella is a decentralized peer-to-peer network used for distributed search of files. Since the network is fully decentralized, peers in the network are called \emph{servents}, a combination of the words servers and clients. Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries. In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available \footnote{These peers can be found on http://gnutellahosts.com.}. Once the peer has joined, there are several messages a servent can send out:

>>>>

		With the second generation onion routing used in Tor, a modified algorithm is used to derive the encryption keys, called telescoping path-building, which also provides perfect forward secrecy. This algorithm is described in section \ref{ss:tor_circuit}.

@@

	\subsection{Low-resource routing attacks}
		Another possible attack on the anonymity of Tor is the so called low-resource routing attack \cite{bauer2007low}. With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resources, thus compromising the anonymity Tor provides. The idea of this attack is that a malicious Onion router can lie about its bandwidth, thus advertising a much higher bandwidth than it actually has. Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry and exit node are chosen is high.

@@

		Rahman \cite{rahman2009survey} proposes several options to build incentives in a peer-to-peer network. The first proposal that is described is the so called Warm-glow Model. This model determines the percentage of free-rides based on the probabilistic population distribution. If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.

@@

		The third proposal is Reciprocity-Based Schemes. Using this approach, a peer maintains a behavior history of other peers in the network. These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity. The former are more suitable for longer relationships between peers. The latter is more scalable but they rely on third party and must handle trust issues themselves.

@@

		Tor currently uses an interactive forward-secret key-exchange protocol called the Tor Authentication Protocol (TAP) \cite{backes2012ace}. This protocol uses telescoping, which means that the initiator negotiates session keys with each successive hop in the circuit. There are several proposals for more efficient key exchange methods. One of them is ACE, an one-way authenticated key exchange protocol. The authors of this methods claim to have a 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the Onion Routers. ACE requires clients to send one extra element in the key exchange. This does not introduce any overhead however, because the element fits in the unused space in a cell.

@@

	\subsection{Gnutella} % ~2000
		Gnutella is a decentralized peer-to-peer network used for distributed search of files. Since the network is fully decentralized, peers in the network are called servents, a combination of the words servers and clients. Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries. In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available \footnote{These peers can be found on http://gnutellahosts.com.}. Once the peer has joined, there are several messages a servent can send out:
